\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{tikz}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Nguyen Ngoc Quy} \\ \vspace{1pt}
    \small
    \raisebox{-0.1\height}\faPhone\ +84 918 211 296 ~
    \href{mailto:pipyakas@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ pipyakas@gmail.com} ~
    \href{https://quynn.dev}{\raisebox{-0.2\height}\faLink\ https://quynn.dev} ~
    \raisebox{-0.1\height}\faMapMarker\ Hanoi, Vietnam
\end{center}

%-----------OBJECTIVE-----------
\section{Summary}
Software Engineer with 5+ years of experience in high-performance C++ systems. Specialist in CI/CD automation, Unreal Engine 5 migrations, and internal infrastructure development. Proven track record of operating independently in global remote environments across multiple time zones.

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Hanoi University of Science and Technology}{Sep 2014 -- Oct 2021}
      {BS in Global ICT (Information and Communication Technology)}{}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Gameloft}{Mar 2021 -- Present}
      {Game Programmer}{}
      \resumeItemListStart
                \resumeItem{Core Engineering: Developed high-performance C++ systems for AAA mobile titles, managed Java-based Android platform integrations, and utilized Python for extensive toolset and pipeline scripting.}
        \resumeItem{Jenkins CI/CD: Architected and maintained the build infrastructure for Sniper Fury, streamlining release stability and deployment pipelines.}
        \resumeItem{Unreal Engine 5: Participated in the critical UI/UX migration for March of Empires, refactoring legacy systems to leverage modern rendering and widget frameworks.}
        \resumeItem{Technical Leadership \& Mentorship: Orchestrated specialized workshops and programming contests integrated with internal architecture while mentoring junior engineers to improve onboarding and documentation standards.}
        \resumeItem{Cross-stack Adaptability: Successfully transitioned across 4+ major project teams (Asphalt, Sniper Fury, March of Empires, DML), mastering diverse legacy and modern tech stacks.}
        \resumeItem{Global Remote Collaboration: Operate independently within a distributed workforce, collaborating effectively with cross-functional teams across international time zones.}
        \resumeItem{English Communication: Utilize fluent business communication to manage stakeholder requirements and technical documentation in a multi-national environment.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages \& Soft Skills:} C++, Java, Python, Fluent English, Remote Autonomy \\ \textbf{Engines \& DevOps:} Unreal Engine 5, Jenkins, Docker, Git, Jira
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
